Hadoop Image Processing Framework

### 2015-03-15 Paper.tex
Finished editing methodology section.

\textbf{Step 3: Process individual image.} For every HImage retrieved in the map task, the algorithm is run on the HImage which is given as the input to the processor module. The HImage retrieves the image as data type(e.g. BufferedImage, Mat image) in the algorithm. Once the image data type is retrieved processing takes place. After processing, the image header data of the original image is appended to the processed image, thereby preserving image header data. The processed image is appended to the temporary bundle generated by the map task.

\textbf{Step 4: Store processed images in an image Bundle.} Every map task generate a image bundle after the map task is completed. Once the map phase is completed there are many bundles. In the reduce phase, all these temporary image bundles are merged into a single large file which contains all the processed images.

\begin{figure}[h]
	\centering
	\includegraphics[width=0.45\textwidth]{pro-node}
	\caption{Single Node running the Processor Module handled by the framework and transparent to user}
	\label{fig:pro-node}
\end{figure}

\subsection{Extracting image bundle using MapReduce}
The framework creates and processes image bundles but there should be a way to extract these images and make them viewable. Generally, Hadoop extracts images from the image bundle iteratively using a single node which is not efficient. To make the process distributed among different nodes we designed an extractor module which can extract images in parallel in all the nodes.

Distribution plays a key role in MapReduce, we want to make use of the nodes effectively to make the process of extraction efficient. In general, the user needs to create custom InputFormat and RecordReader classes to specify the MapReduce job and distribute the input among nodes. In order to over come this the framework takes care of these Custom InputFormat and RecordReader to make working with hadoop more easier.

There is often a confusion to where the images need to be extracted. The images can be extracted to the local file system of the node or hadoop file system. The framework overcomes the problem by providing a flexibility to choose.

The working of Extractor module is explained below.

\textbf{Step 1: Input the image bundle to be extracted.} The image bundle that needs to extracted is passed as a parameter to the Extractor module. Along with it the user can send an optional parameter to where the images need to be extracted (defaults to local file system). After the input the image bundle is distributed across nodes as individual map task. Each map task will extract the image in to the filesystem.

\begin{figure}[h]
	\centering
	\includegraphics[width=0.45\textwidth]{ext-map}
	\caption{Individual Map Task of Extractor Module}
	\label{fig:ext-map}
\end{figure}

\textbf{Step 2: Split Image bundle across nodes}
The input image bundle split across nodes using the custom input format and record reader classes for maximum throughput. Once a Map task starts a HImage object is retrieved.

\textbf{Step 3: Extract individual image}
The obtained HImage object is retrieved as image bytes and the image bytes are stored into the file based on its image type. The Extractor module doesn't have a reduce phase.

\begin{figure}[h]
	\centering
	\includegraphics[width=0.45\textwidth]{ext-node}
	\caption{Single node running the Extractor Module handled by the framework and transparent to user}
	\label{fig:ext-node}
\end{figure}

>>>>

\textbf{Step 3: Process individual image.}  The processing algorithm
devised by the user and provided as input to the Processing Module is
applied to every HImage retrieved in the map task.  The HImage
provides its image data in the data format (e.g. Java BufferedImage,
OpenCV Mat, etc.) requested by the user and used by the processing
algorithm. Once the image data type is retrieved, processing takes
place. After processing, the preserved image header data from the
original image is appended to the processed image. The processed image
is appended to the temporary bundle generated by the map task.

\textbf{Step 4: Store processed images in an image bundle.} Every map
task generates an image bundle upon completion of its processing.
Once the map phase is completed there are many bundles scattered
across the computing cluster.  In the reduce phase, all of these
temporary image bundles are merged into a single large file which
contains all the processed images.

\begin{figure}[h]
  \centering
  \includegraphics[width=0.45\textwidth]{pro-node}
  \caption{Single node running the Processor Module (handled by
    the framework and transparent to user)}
  \label{fig:pro-node}
\end{figure}

\subsection{Extracting image bundles using MapReduce}
In addition to creating and processing image bundles, the framework
provides a method for extracting and viewing these images.  Generally,
Hadoop extracts images from an image bundle iteratively, inefficiently
using a single node for the task. To address this inefficiency, we
designed an Extractor module which extracts images in parallel across
all available nodes.

Distribution plays a key role in MapReduce; we want to make effective
and efficient use of the nodes in the computing cluster.  As
previously mentioned in the description of the Processor module, a
user working in a generic Hadoop system must again devise custom
InputFormat and RecordReader classes in order to facilitate
distributed image extraction.  The Hadoop Image Processing Framework
provides this functionality for the extraction task as well, providing
much greater ease of use for the development of image processing
applications.

Organizing and specifying the final location of extracted images in a
large distributed task can be confusing and difficult.  Our framework
provides this functionality, and allows the user simply to specify
whether images should be extracted to a local file system or reside on
the Hadoop DFS.

The process of the Extractor module is explained below:

\textbf{Step 1: Input the image bundle to be extracted.} The image
bundle specified for extraction is passed as a parameter to the
Extractor module.  In addition, the user can include an optional
parameter specifying the images' final location (defaults to local
file system).  The image bundle is then distributed across the nodes
as individual map tasks. Each map task will extract the requisite
images onto the specified filesystem.

\begin{figure}[h]
  \centering
  \includegraphics[width=0.45\textwidth]{ext-map}
  \caption{Individual map task of Extractor Module}
  \label{fig:ext-map}
\end{figure}

\textbf{Step 2: Split Image bundle across nodes} The input image
bundle is split across available nodes using the framework's custom
input format and record reader classes for maximum throughput. Once a
map task starts, HImage objects are retrieved.

\textbf{Step 3: Extract individual image} The image bytes obtained
from each HImage object are stored onto the filesystem in the
appropriate file format based on its image type.  The Extractor module
lacks a reduce phase.

\begin{figure}[h]
  \centering
  \includegraphics[width=0.45\textwidth]{ext-node}
  \caption{Single node running the Extractor Module (handled by the
    framework and transparent to the user)}
  \label{fig:ext-node}
\end{figure}
